---
title: "Lab5"
author: "Saman Zahid"
date: "December 11, 2018"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Question 1

```{r}
#install.packages("devtools")
library(devtools)
#install_github("mategarb/R.ROSETTA")
library(R.ROSETTA)

```

## Question 2


```{r pressure, echo=FALSE}

View(autcon)
decision_sum <- table(autcon$decision)

```

total number of features = 36 -1 = 35, since last one is class.


### For distribution:
```{r}

control_ratio <- as.numeric(decision_sum[1])/146
autism_ratio <- as.numeric(decision_sum[2])/146

```

Since controls and autism are nearly around 50% distributed thus the distribution is balanced


```{r}
autconDefault = rosetta(autcon)

rules <- autconDefault$main
quality <- autconDefault$quality
quality

```

Part a - Cross validation: Partition the data into equally sized subsets and perform model assesment.
**Rosetta performs 10 fold cross validation by default**

Part b - "Johnson" is the default reduction method. Reducer is used to find the dependencies in data.

Part c - The default method of discretization is **EqualFrequency**. It partitions the range of features a(x) into (n+1) intervals by placing cuts between features, so that each interval has the same number of objects. 
The default number of bins is 3.

Part d -

```{r}
paste("Accuracy of model : " , quality$Accuracy.Mean)
```
